\chapter{Components}
\section{Entity}

All objects that the user wants to create get created via the Entity class.



The constructor of Entity takes these arguments:

\begin{itemize}
	\item name
    \item body
    \item physics
    \item collisionDetection
    \item audioManager
    \item sprite
\end{itemize}


Example of how to create a $Entity$:

\begin{lstlisting}
class Pipe {
  constructor(startPos, topPos, height, width) {
    this.len;
    this.entity = new Entity(
      "Bottom pipe",
      new Body(this, 1920 + startPos, topPos, height, width),
      new Physics(this, -8.85, 0),
      new CollisionDetection(this),
      null
    );
  }
}
\end{lstlisting}


\section{Body}
Body class is the body of the entity.  

The constructor of Body takes these arguments:

\begin{itemize}
	\item entity
    \item left
    \item top
    \item height
    \item width
\end{itemize}

The body class contains only setters and getters for these parameters.

\begin{lstlisting}
class Bird {
  constructor() {
    this.entity = new Entity(
      "Bird",
      new Body(this, 300, 540, 100, 100),
      }
}
\end{lstlisting}

Here is a small example of how to move the entity bird:
\begin{lstlisting}

if (this.getBody().getTop() > 1040) {
      this.getBody().setTop(400);
      this.getBody().setLeft(300);
    }
\end{lstlisting}

\section{CollisionDetection}
To check for collitionDectection use:
\begin{lstlisting}
  checkForCollision(otherEntity)
\end{lstlisting}

Example of this can be:
\begin{lstlisting}

let hasPlayerCollided = player
          .getCollisionDetection()
          .checkForCollision(this.state.playerArr[index].getEntity());
\end{lstlisting}


\section{Physics}

\section{AudioManager}
example to use audioManager:

Object:
\begin{lstlisting}
    new AudioManager([
        ResMan.getAudioPath("soundEffect1.mp3"),
        ResMan.getAudioPath("soundEffect2.mp3"),
        ResMan.getAudioPath("soundEffect3.mp3")
      ]),    
    this.enum = {
      BIRD_JUMPS: 0,
      BIRD_SCORE: 1,
      BIRD_DIES: 2
};
\end{lstlisting}

Then if something happens:
\begin{lstlisting}

object.getAudioManager().play(2); // testing!!!
\end{lstlisting}


\section{Sprite}
\section{ResourceManager}

To use the ResourceManager simply import the class and use it like this:

\begin{lstlisting}
ResourceManager.getImagePath("background.png")
\end{lstlisting}

\begin{lstlisting}
ResourceManager.getAudioPath("one.mp3")
\end{lstlisting}

\begin{lstlisting}
ResourceManager.getSpritePath("birds.png")
\end{lstlisting}

The $ResourceManager$ uses a default paths:

\begin{itemize}
	\item ../resources/image/
    \item ../resources/audio/
    \item ../resources/sprite/
\end{itemize}

You can change these paths in the $resourceManager$ file

\section{Background}

To use the $Background$ component, simply add it to the component.

\begin{lstlisting}
<Background
              height={1080}
              width={1920}
              speed={0.5}
              image={ResourceManager.getImagePath("background.png")}
            >
              {" "}
            </Background>{" "}
\end{lstlisting}

$ackground$ contains $defaultProps$, so it is not needed to set $height$, $width$ and $speed$. To set a image you can either use the $ResourceManager$ or simply import a image.

\section{HUD}
To use the HUD simply add the HUD component
\begin{lstlisting}
<HUD score={this.state.score} position={"tc"} />{" "}
\end{lstlisting}

Where score is a score variable from the game.

\section{Menu}
To use the menu, simply import the component into the file you want.

\begin{lstlisting}
<Menu showMenu={this.state.showMenu}
\end{lstlisting}

Using ${this.state.showMenu}$ gives you the option of toggling it on and off, depending of a boolean $showMenu$.

To add more menu options, simply add more items into the $menuItems$, and use $handleClick(e)$ for the event.

\section{ScoreBoard}
To use scoreboard simply add:

\begin{lstlisting}
<ScoreBoard />
\end{lstlisting}

To get the score from the game, $context$ is recommended, as it is shown in the $flappy$ demo, since normally a $menuItem$ shows a scoreboard.

\section{Logger}
To use the logger simply use:

\begin{lstlisting}
Logger.setText("flappy.js", `score: ${this.state.score}`);
\end{lstlisting}

where first argument is the name of file and second argument is what you want to log.

Then you can add this to the game:
\begin{lstlisting}
<LoggerManager /> 
\end{lstlisting}

  